---
title: "PeerAssessmentML"
author: "Florian Refardt"
date: "Sunday, October 25, 2015"
output: html_document
---


##Validation

The given data set will be sampled into two subsamples. A variable called samplesTraining will hold 75% of the original data and samplesTesting the other 25%. The model will be fitted to the samplesTraining set and then tested on the original testing data.


##Expected outcome

The expected value of the outcome-sample error will correspond to the expected number of missclassified total observations in the Test data set.


```{r}
library(caret)
library(ggplot2)
library(randomForest)

getwd()

```


```{r }

### Somehow only local .csv files work with R Markdown

#trainingData <- read.csv("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv", na.strings=c("", "NA", "NULL"), header=TRUE, sep = ",")
#testingData <- read.csv("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv", na.strings=c("", "NA", "NULL"), header=TRUE, sep = ",")


trainingData <- read.csv("C:/Users/fref/Documents/GitHub/predmachlearn/pml-training.csv", na.strings=c("", "NA", "NULL"), header=TRUE, sep = ",")

testingData <- read.csv("C:/Users/fref/Documents/GitHub/predmachlearn/pml-testing.csv", na.strings=c("", "NA", "NULL"), header=TRUE, sep = ",")

```


```{r}

# Show the 5 diffrent classes and its frequency

plot(trainingData$classe, col="blue", main="Frequency of the 5 different classes", xlab="classes", ylab="Frequency")
```

```{r eval=FALSE}
summary(trainingData)
summary(testingData)
```


```{r}

# Delete columns with NA values
trainingDataCleaned <- trainingData[,colSums(is.na(trainingData)) == 0]
testingDataCleaned <- testingData[,colSums(is.na(testingData)) == 0]

#summary(trainingDataCleaned)



# Clean non numeric variables for prediction
trainingDataCleaned <- trainingDataCleaned[,-c(1:7)]
#trainingDataCleaned <- which(lapply(trainingDataCleaned,class) %in% c('numeric'))
testingDataCleaned <- testingDataCleaned[,-c(1:7)]

dim(trainingDataCleaned)
dim(testingDataCleaned)

#Building the sample data
samplesAll <- createDataPartition(y=trainingDataCleaned$classe, p=0.75, list=FALSE)
samplesTraining <- trainingDataCleaned[samplesAll, ] 
samplesTesting <- trainingDataCleaned[-samplesAll, ]


modelRF <- randomForest(classe ~. , data=samplesTraining, method="class")

# Predicting:
predictionRF <- predict(modelRF, samplesTesting, type = "class")

# Test results on subTesting data set:
confusionMatrix(predictionRF, samplesTesting$classe)

```

## Final Prediction

Final prediction on original testing data.

```{r}

predictionRF_Final <- predict(modelRF, testingDataCleaned, type = "class")
predictionRF_Final

```

